Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-05-24 analysis/paper/paper.Rmd
Figure cofactors

---
title: "Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry"
author:
  - Wojciech Francuzik^1^
  - Sabine Dölle-Bierke^1^
  - Franziska Ruëff^2^ 
  - Claudia Pföhler^3^
  - Kathrin Scherer Hofmeier^4^
  - Margitta Worm^1^
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    #bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
---

@@

```{r insectstime, fig.cap="A: Proportion of anaphylaxis cases elicited by specific insects according to the month in which the reaction occured. Less frequent insects were groupeped together as 'other'. B: The proportion of insect elicited cases to ceses elicited by other triggers considering patient's age. C: Geographical differences in the most common eliciotors of IVA. Countries which reported less than 10 cases of anaphylaxis due to insect venom were not illustrated in this figure."}
fig_basic
```

@@

```{r}
crammerElicitorBinvsSympt[1:15,] %>% arrange(desc(CV)) %>% knitr::kable()

crammerElicitorBinvsSympt[1:15,] %>% arrange(desc(CV)) %>%
  filter(CV<0.3,
         CV>0.15) %>% 
  ggplot(aes(reorder(var,-CV),CV))+
  geom_col()+
  theme(axis.text.x = element_text(angle=90))
```

Patients with Insect Venom Allergy had a lot more cardiologic symptoms than anaphylaxis cases that were elicited through other triggers.  
Dizziness, Loss of consciousness hypotension, collapse, Throat tightness and nausea were a lot more often associated with the insect cases.

Forest plot ! Risk that the symptom will occure given that the reaction was elicited by Insects or not

@@

```{r flow}
knitr::include_graphics("../figures/flow.png")
```

```{r figforestcofactors}
knitr::include_graphics("../figures/figForest.png")
```

```{r figforestcofactorskids}
knitr::include_graphics("../figures/kidsForest.png")
```

```{r figforestcofactorsadults}
knitr::include_graphics("../figures/adultsForest.png")
```

```{r}
mosaic(d_organ_sum~d_elicitor_gr5,data=rdb)
```

```{r}
mosaic(d_severity_rm~d_elicitor_gr5,data=rdb)
```

```{r}
hypotensionPlot
```

```{r}
cramerPlot
```

```{r}
plot.Cramer(supraCramerFun(data =rdbp,
               vars =c( "q_114",
               "q_112_incontinence",
               "q_114_dizziness",
               "q_112_abdominal_pain",
               "q_114_loss_of_consciousness",
               "q_114_hypotension_collapse_v5",
               "q_114_reductions_of_alertness",
               "q_111_angioedema",
               "q_113_wheezing_expiratory_distress_v5"),
               grouping = "grouping",
               subset = "d_age_gr2"))

```{r}
plot.Cramer(cramerFun(data =rdbp,
               vars=c("q_114",
               "q_112_incontinence",
               "q_114_dizziness",
               "q_112_abdominal_pain",
               "q_114_loss_of_consciousness",
               "q_114_hypotension_collapse_v5",
               "q_114_reductions_of_alertness",
               "q_111_angioedema",
               "q_113_wheezing_expiratory_distress_v5"),
               grouping = "grouping"))
```

```{r}
tryptase_plot(rdb)+
  scale_x_log10()+
  facet_grid(~d_age_gr2)

```{r reactionmonthincountries, fig.cap="Proportional insect venom induced anaphylaxis to specific insects during a year according to countries.", fig.height=8,fig.width=5}
plot_MOR+
  facet_grid(d_centres_country~.)
```

```{r}
plot_MOR
```

```{R adrenalineuse, fig.cap = "The proportion of insect venom elicited anaphylaxis cases that were treated with adrenaline in comparison to other elicitors."}
fig_adrenuse1
```

```{r figsymptoms, fig.cap="Symptoms of insect venom anaphylaxis (IVA) compared to other elicitors",fig.width=8}
fig_symptoms
```

>>>>

---
title: "Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry"
author:
  - Wojciech Francuzik^1^
  - Sabine Dölle-Bierke^1^
  - Franziska Ruëff^2^ 
  - Claudia Pföhler^3^
  - Kathrin Scherer Hofmeier^4^
  - Margitta Worm^1^
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    #bookdown::html_document2:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
---

@@

@@

Patients with Insect Venom Allergy had a lot more cardiologic symptoms than anaphylaxis cases that were elicited through other triggers.  
Dizziness, Loss of consciousness hypotension, collapse, Throat tightness and nausea were more often associated with the insect cases.

<!-- Forest plot ! Risk that the symptom will occure given that the reaction was elicited by Insects or not -->

@@

```{r flow,fig.width=6,fig.height=4}
knitr::include_graphics("../figures/flow.png")
```

```{r insectstime, fig.cap="A: Proportion of anaphylaxis cases elicited by specific insects according to the month in which the reaction occured. Less frequent insects were groupeped together as 'other'. B: The proportion of insect elicited cases to ceses elicited by other triggers considering patient's age. C: Geographical differences in the most common eliciotors of IVA. Countries which reported less than 10 cases of anaphylaxis due to insect venom were not illustrated in this figure.",fig.height=4,fig.width = 7}
fig_basic
```

```{R adrenalineuse, fig.cap = "The proportion of insect venom elicited anaphylaxis cases that were treated with adrenaline in comparison to other elicitors.",fig.height=4,fig.width = 6}
fig_adrenuse1
```

```{r figsymptoms, fig.cap="Symptoms of insect venom anaphylaxis (IVA) compared to other elicitors",fig.width=9.5,fig.height = 6}
fig_symptoms
```

```{r figcofactors, fig.cap="Cofactors of insect venom anaphylaxis ad their relationship to severity of a reaction",fig.width=4.2,fig.height = 6}
cof_fig
```
